
---
title: "ML Project"
author: "Suzana Iacob"
date: "21/11/2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(dplyr)
library(rpart)
library(rpart.plot)
library(caTools)
library(caret) 
library(gbm)
library(glmnet)
library(randomForest) 
library(matrixStats)
library(dplyr)
library(cvar)
library(caret)
library(glmnet)
library(dplyr)
library(ggplot2)
library(tidyr)
library(lars)
library(leaps)
library(gbm)
library(randomForest) 
library(rpart) 
library(ggplot2)
library(rpart.plot)
library(caTools)
library(caret)
library(gbm)
library(ROCR)
```

## Import Processed Data


```{r import}
utilities_train <- read.csv("utilities_s1_d1_train.csv")
utilities_test <- read.csv("utilities_s1_d1_test.csv")
global_utilities <- rbind(utilities_train,utilities_test )
utilities_train$best_treatment = as.factor(utilities_train$best_treatment)
utilities_test$best_treatment = as.factor(utilities_test$best_treatment)
table(utilities_train$best_treatment)
```

## Model

```{r model}
utilities_tree = rpart(best_treatment ~., data=utilities_train,cp=0.002, minbucket=10, method="class")
prp(utilities_tree, digits = 0, varlen = 0, faclen = 0)
```


### DATA PERTURBATION

```{r perturbation}
means_global = t(colMeans(global_utilities[,1:56]))
sds_global = t(colSds(as.matrix(global_utilities[,1:56])))
colnames(sds_global) <- colnames(means_global)
write.csv(means_global, "means_global.csv")
write.csv(sds_global, "sds_global.csv")
```


### PERTURBATING THE TEST SET WITH 10% OF THE STANDARD DEVIATION

```{r test perturbation}
utilities_test_perturbed = data.frame(utilities_test$best_treatment)
m = length(colnames(utilities_test)) #We don't perturb the final observation
for (i in 1:(m-1)){
  perturbation = data.frame(utilities_test[,m-i] + (means_global[m-i]-rnorm(3000,means_global[m-i], 0*sds_global[m-i] )))
  utilities_test_perturbed = data.frame(perturbation,utilities_test_perturbed)
  }
colnames(utilities_test_perturbed) = colnames(utilities_test)
```
```{r prediction assessment}
prediction_perturbed = predict(utilities_tree, newdata = utilities_test_perturbed, type="class")
matrix_perturbed = table(utilities_test_perturbed$best_treatment, prediction_perturbed)
matrix_perturbed
accuracy_pertubed = print((matrix_perturbed[1,1]+matrix_perturbed[2,2]+matrix_perturbed[3,3])/nrow(utilities_test))
```


### ASSESSMENT OF THE IMPACT OF A PERTURBATION ON ALL FEATURES


```{r }
seq_pertubation = seq(from = 0, to = 3, by = 0.1)
m = length(colnames(utilities_test)) 
n = nrow(utilities_test) #Here it's 3000
accuracy_p <- c()
for (p in seq_pertubation){
      utilities_test_perturbed = data.frame(utilities_test$best_treatment)
      for (i in 1:(m-1)){
      perturbation = data.frame(utilities_test[,m-i] + (means_global[m-i]-rnorm(n,means_global[m-i], p*sds_global[m-i] )))
      utilities_test_perturbed = data.frame(perturbation,utilities_test_perturbed)
      
      }
    
      colnames(utilities_test_perturbed) = colnames(utilities_test)
     
      prediction_perturbed = predict(utilities_tree, newdata = utilities_test_perturbed, type="class")
      matrix_perturbed = table(utilities_test_perturbed$best_treatment, prediction_perturbed)
      accuracy_pertubed = (matrix_perturbed[1,1]+matrix_perturbed[2,2]+matrix_perturbed[3,3])/n
      
      accuracy_p <- c(accuracy_p, accuracy_pertubed )
  
}
```
```{r }
plot_data <- data.frame(seq_pertubation,accuracy_p)
plot_pertubation <- ggplot(plot_data) +
  geom_line(aes(x = seq_pertubation, y = accuracy_p ), color = "red")  +
  ggtitle("Accuracy evolution with global perturbation") +
  ylab("Accuracy") + xlab("standard deviation perturbation") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave("accuracy_evolution_with_perturbation.png")
plot_pertubation
```

### ASSESSMENT OF THE PERTUBATION WITH THE NUMBER OF LABELS PERFURBED

We select randomly a number of labels to perturb with one standard deviation, then we perturb them with a different ratio of standard deviation.

Question: How do we select these elements? We do a random forest that gives us the variable importance of each variables, then we select based on this importance.

```{r random forest for importance}
rf.mod = randomForest(best_treatment ~., data=utilities_train, method="class")
importance.rf <- data.frame(imp=importance(rf.mod))
importance.rf$position <- seq(from = 1, to = 56, by = 1)
importance.rf.ordered <- importance.rf[order(-importance.rf$MeanDecreaseGini), ,drop = FALSE]
importance_features = data.frame(importance.rf.ordered)
write.csv(importance_features, "importance_features.csv")
```
```{r}
number_label = seq(from = 1, to = 20, by = 1)
p = 0.5 #number of sd to perturb with
ind_accuracy05 <- c()
for (number in number_label) {
    
    index_pertubed = importance.rf.ordered[1:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    ind_accuracy05 <- c(ind_accuracy05, ind_accuracy_pertubed)
}
```


```{r }
number_label = seq(from = 1, to = 20, by = 1)
p = 1 #number of sd to perturb with
ind_accuracy1 <- c()
for (number in number_label) {
    index_pertubed = importance.rf.ordered[1:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    ind_accuracy1 <- c(ind_accuracy1, ind_accuracy_pertubed)
}
```

```{r }
number_label = seq(from = 1, to = 20, by = 1)
p = 1.5
ind_accuracy15 <- c()
for (number in number_label) {
   
    #number of sd to perturb with
    
    index_pertubed = importance.rf.ordered[1:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    ind_accuracy15 <- c(ind_accuracy15, ind_accuracy_pertubed)
}
```


### PLOT OF THE RESULTS

```{r }
data_plot_2 <- data.frame(number_label,ind_accuracy05, ind_accuracy1, ind_accuracy15)
data_plot_2 %>%
  gather(key,value, ind_accuracy05, ind_accuracy1, ind_accuracy15) %>%
   ggplot(aes(x = number_label, y=value, colour=key)) +
  geom_line() +
   ylim(0.5, 0.75) +
  ylab("Accuracy") + xlab("Number of labels perturbed") +
  ggtitle("Accuracy evolution according to the number of features perturbed") +
  theme(plot.title = element_text(hjust = 0.5)) +
   scale_color_manual(values=c("#f08080", "#00aee7", "#5ac18e") )+
  ggsave("evolution_to_features.png") 
 
```


COMMENT: The performance doesn't depend on the number of variables we pertub but the variables them self. Let's perturb the variables exluding the three most important ones.

```{r perturbation exluding the most important ones}
number_label = seq(from = 4, to = 24, by = 1)
p = 0.5 #number of sd to perturb with
d_ind_accuracy05 <- c()
for (number in number_label) {
    
    index_pertubed = importance.rf.ordered[4:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    d_ind_accuracy05 <- c(d_ind_accuracy05, ind_accuracy_pertubed)
}
p = 1 #number of sd to perturb with
d_ind_accuracy1 <- c()
for (number in number_label) {
    index_pertubed = importance.rf.ordered[4:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    d_ind_accuracy1 <- c(d_ind_accuracy1, ind_accuracy_pertubed)
}
d_ind_accuracy15 <- c()
for (number in number_label) {
   
    #number of sd to perturb with
    
    index_pertubed = importance.rf.ordered[4:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    d_ind_accuracy15 <- c(d_ind_accuracy15, ind_accuracy_pertubed)
}
```

```{r }
number_label_3 <- number_label-4
data_plot_3 <- data.frame(number_label_3,d_ind_accuracy05, d_ind_accuracy1, d_ind_accuracy15)
data_plot_3 %>%
  gather(key,value, d_ind_accuracy05, d_ind_accuracy1, d_ind_accuracy15) %>%
   ggplot(aes(x = number_label_3, y=value, colour=key)) +
  geom_line() +
   ylim(0.5, 0.75) +
  xlab("Accuracy") + ylab("Number of labels perturbed") +
  ggtitle("Evolution - excluding the 3 most important features") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave("evolution_to_features_2.png") +
  scale_color_manual(values=c("#f08080", "#00aee7", "#5ac18e"))
```

COMMENT: This has very important implications, it implies that we should control only the three first variables to be robust to data perturbation. This three variables are : Standard.relapse...No.adverse.effect, Standard.relapse...Non.serious.adverse.effect.only, Reduced.relapse...Non.serious.adverse.effect.only	


### MODEL'S ROBUSTIFICATION

We robustify by generating pertubation in the data set for this three variables.

```{r robust_train_generation}
means_train = t(colMeans(global_utilities[,1:56]))
sds_train = t(colSds(as.matrix(global_utilities[,1:56])))
colnames(sds_train) <- colnames(means_global)
index_important = importance.rf.ordered[1:3,2]
utilities_train_05 <- data.frame(utilities_train)
utilities_train_1 <- data.frame(utilities_train)
utilities_train_15 <- data.frame(utilities_train)
n = nrow(utilities_train)
for (index in index_important){
     
      perturbation_ind_05 = data.frame(utilities_train[,index] + (means_train[index]-rnorm(n,means_train[index], 0.5*sds_train[index])))
      perturbation_ind_1 = data.frame(utilities_train[,index] + (means_train[index]-rnorm(n,means_train[index], 1*sds_train[index])))
      perturbation_ind_15 = data.frame(utilities_train[,index] + (means_train[index]-rnorm(n,means_train[index], 1.5*sds_train[index])))
      
      utilities_train_05[,index] = perturbation_ind_05
      utilities_train_1[,index] = perturbation_ind_1
      utilities_train_15[,index] = perturbation_ind_15
}
robust_utilities_train = rbind(utilities_train, utilities_train_05, utilities_train_1, utilities_train_15 )
write.csv(robust_utilities_train, "robust_utilities_train.csv")
```

```{r train on the robust utilities}
robust_utilities_tree = rpart(best_treatment ~., data=robust_utilities_train,cp=0.002, minbucket=10, method="class")
prp(robust_utilities_tree, digits = 0, varlen = 0, faclen = 0)
```

### FIRST ASSESSMENT OF THE ROBUSTIFIED MODEL


```{r prediction}
prediction = predict(robust_utilities_tree, newdata = utilities_test, type="class")
matrix = table(utilities_test$best_treatment, prediction)
matrix
print((matrix[1,1]+matrix[2,2]+matrix[3,3])/nrow(utilities_test))
```


### ASSESSMENT OF THE IMPACT OF A PERTURBATION ON ALL FEATURES WITH ROBUST DATA


```{r}
seq_pertubation = seq(from = 0, to = 3, by = 0.1)
m = length(colnames(utilities_test)) 
n = nrow(utilities_test) #Here it's 3000
robust_accuracy_p <- c()
for (p in seq_pertubation){
      utilities_test_perturbed = data.frame(utilities_test$best_treatment)
      for (i in 1:(m-1)){
      perturbation = data.frame(utilities_test[,m-i] + (means_global[m-i]-rnorm(n,means_global[m-i], p*sds_global[m-i] )))
      utilities_test_perturbed = data.frame(perturbation,utilities_test_perturbed)
      
      }
    
      colnames(utilities_test_perturbed) = colnames(utilities_test)
     
      prediction_perturbed = predict(robust_utilities_tree, newdata = utilities_test_perturbed, type="class")
      matrix_perturbed = table(utilities_test_perturbed$best_treatment, prediction_perturbed)
      accuracy_pertubed = (matrix_perturbed[1,1]+matrix_perturbed[2,2]+matrix_perturbed[3,3])/n
      
      robust_accuracy_p <- c(robust_accuracy_p, accuracy_pertubed )
  
}
```
```{r }
plot_data <- data.frame(seq_pertubation,robust_accuracy_p, accuracy_p)
plot_data %>%
  gather(key,value, robust_accuracy_p, accuracy_p) %>%
   ggplot(aes(x = seq_pertubation, y=value, colour=key)) +
  geom_line() +
   ylim(0.5, 0.75) +
  xlab("Perturbation with SD") + ylab("Accuracy") +
  ggtitle("Comparison of perturbation impact") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave("robust_accuracy_evolution_with_perturbation.png")
```

COMMENT: Robustifying the data with only the three most important features gives impressive resistance to data perturbation. The first lower performance is due to a more complex data generated while robustifying the CART, but where the data is perturbed at higher values, the robust model cleary outperforms the basic one.

```{r}
number_label = seq(from = 1, to = 20, by = 1)
p = 0.5 #number of sd to perturb with
rob_ind_accuracy05 <- c()
for (number in number_label) {
    
    index_pertubed = importance.rf.ordered[1:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(robust_utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    rob_ind_accuracy05 <- c(rob_ind_accuracy05, ind_accuracy_pertubed)
}
```


```{r}
number_label = seq(from = 1, to = 20, by = 1)
p = 1 #number of sd to perturb with
rob_ind_accuracy1 <- c()
for (number in number_label) {
    index_pertubed = importance.rf.ordered[1:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(robust_utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    rob_ind_accuracy1 <- c(rob_ind_accuracy1, ind_accuracy_pertubed)
}
```

```{r }
number_label = seq(from = 1, to = 20, by = 1)
p = 1.5
rob_ind_accuracy15 <- c()
for (number in number_label) {
   
    #number of sd to perturb with
    
    index_pertubed = importance.rf.ordered[1:number,2]
    
    ind_utilities_test_perturbed <- data.frame(utilities_test)
    for (index in index_pertubed){
          perturbation_ind = data.frame(utilities_test[,index] + (means_global[index]-rnorm(n,means_global[index], p*sds_global[index])))
          
          ind_utilities_test_perturbed[,index] = perturbation_ind
      
    }
    
    ind_prediction_perturbed = predict(robust_utilities_tree, newdata = ind_utilities_test_perturbed, type="class")
    
    ind_matrix_perturbed = table(ind_utilities_test_perturbed$best_treatment, ind_prediction_perturbed)
    
    
    ind_accuracy_pertubed = (ind_matrix_perturbed[1,1]+ind_matrix_perturbed[2,2]+ind_matrix_perturbed[3,3])/n
      
    rob_ind_accuracy15 <- c(rob_ind_accuracy15, ind_accuracy_pertubed)
}
```


### PLOT OF THE RESULTS

```{r }
data_plot_5 <- data.frame(number_label,ind_accuracy05, ind_accuracy1, ind_accuracy15, rob_ind_accuracy05, rob_ind_accuracy1, rob_ind_accuracy15)
data_plot_5 %>%
  gather(key,value, ind_accuracy05, ind_accuracy1, ind_accuracy15,rob_ind_accuracy05, rob_ind_accuracy1, rob_ind_accuracy15) %>%
   ggplot(aes(x = number_label, y=value, colour=key)) +
  geom_line() +
   ylim(0.5, 0.75) +
  xlab("Accuracy") + ylab("Number of labels perturbed") +
  ggtitle("Robust Accuracy evolution according to the number of features perturbed") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave("robust_evolution_to_features.png") +
  scale_color_manual(values=c("#f08080", "#00aee7", "#5ac18e","#e51635", "#273b66", "#336633"))
```

### Comparison with Multinomial glmnet

```{r }
multi_threshold<- function(pred, actual_values){
  sequence = seq(0,1, by=0.05)
  n = length(actual_values)
  values = c()
  accuracy_max = 0
  for (i in 1:length(sequence)){
      prediction_val = c()
      thresh = sequence[i]
      for (j in 1:nrow(pred)) {
          val1 = pred[j,1]
          val2 = pred[j,2]
          val3 = pred[j,3]
          
         
          if(thresh>val2){
            prediction_val <- c(prediction_val, 3)
          }
          if(thresh<=val2){
            if (thresh<=val1){
              prediction_val <- c(prediction_val, 1)
            }
            else{
              prediction_val <- c(prediction_val, 2)
            }
          }
          
          
      }
      
    table_val = table(actual_values, prediction_val)
    values_pred = as.numeric(colnames(table_val))
    for (k in (1:length(values_pred))){
      good_pred = table_val[values_pred[k],k]
    }
    
     accuracy_thresh = good_pred/n
      
    if (accuracy_thresh>accuracy_max){
       best_thresh = thresh
       accuracy_max = accuracy_thresh
      best_pred = prediction_val
     }
     
  }
   return( best_thresh )
}
threshold_accuracy <- function(pred, actual_values, thresh){
  
  n = length(actual_values)
      prediction_val = c()
      for (j in 1:nrow(pred)) {
          val1 = pred[j,1]
          val2 = pred[j,2]
          val3 = pred[j,3]
          
         
          if(thresh>val2){
            prediction_val <- c(prediction_val, 3)
          }
          if(thresh<=val2){
            if (thresh<=val1){
              prediction_val <- c(prediction_val, 1)
            }
            else{
              prediction_val <- c(prediction_val, 2)
            }
          }
          
          
      }
      
    table_val = table(actual_values, prediction_val)
    values_pred = as.numeric(colnames(table_val))
    for (k in (1:length(values_pred))){
      good_pred = table_val[values_pred[k],k]
    }
    
     accuracy_thresh = good_pred/n
  
   return( accuracy_thresh )
}
threshold_prediction <- function(pred, actual_values, thresh){
      n = length(actual_values)
      prediction_val = c()
      for (j in 1:nrow(pred)) {
          val1 = pred[j,1]
          val2 = pred[j,2]
          val3 = pred[j,3]
          if(thresh>val2){
            prediction_val <- c(prediction_val, 3)
          }
          if(thresh<=val2){
            if (thresh<=val1){
              prediction_val <- c(prediction_val, 1)
            }
            else{
              prediction_val <- c(prediction_val, 2)
            }
          }
      }
   return( prediction_val )
}
```



```{r }
x.train = model.matrix(best_treatment ~., data=utilities_train)
x.test = model.matrix(best_treatment ~., data=utilities_test)
y.train = utilities_train$best_treatment
y.test = utilities_test$best_treatment
set.seed(1)
#glm_treatment.cv <- cv.glmnet(x.train, y.train, alpha=1, family="multinomial", intercept = F, nfolds = 5)
        
#glm_treatment.min <- glm_treatment.cv$lambda.min
#glm_treatment.1se <- glm_treatment.cv$lambda.1se
   
glm_treatment.min = 0.001029396
glm_treatment.1se = 0.01156345
glm_treatment <- glmnet(x.train,y.train,alpha=1,family="multinomial", lambda = glm_treatment.min, intercept = F)
# Definition of threshold
pred_in <- predict(glm_treatment,newx=x.train,type = 'response')
pred_in.df <- data.frame(pred_in)
best_threshold <- multi_threshold(pred_in.df, y.train)
### OUT-SAMPLE
pred <- data.frame(predict(glm_treatment,newx=x.test,type = 'response'))
best_out_accuracy <- threshold_accuracy(pred, y.test, 0.5)
```
```{r}
multi_pred <- function(pred){
    prediction <- c()
    for (i in 1:nrow(pred)) {
      val <- c(pred[i,1], pred[i,2], pred[i,3])
      prediction <- c(prediction, which.max(val))
    }
    return(prediction)
}
```

```{r}
seq_pertubation = seq(from = 0, to = 3, by = 0.1)
m = length(colnames(utilities_test)) 
n = nrow(utilities_test) #Here it's 3000
robust_accuracy_p <- c()
for (p in seq_pertubation){
      utilities_test_perturbed = data.frame(utilities_test$best_treatment)
      for (i in 1:(m-1)){
      perturbation = data.frame(utilities_test[,m-i] + (means_global[m-i]-rnorm(n,means_global[m-i], p*sds_global[m-i] )))
      utilities_test_perturbed = data.frame(perturbation,utilities_test_perturbed)
      
      }
    
      colnames(utilities_test_perturbed) = colnames(utilities_test)
      
      x.test.perturbed = model.matrix(best_treatment ~., data=utilities_test_perturbed)
      y.test.perturbed  = utilities_test_perturbed$best_treatment
     
      prediction_perturbed = data.frame(predict(glm_treatment,newx=x.test.perturbed,type = 'response'))
      
      prediction_val = multi_pred(prediction_perturbed)
     
      table_val = table(y.test.perturbed, prediction_val)
      values_pred = as.numeric(colnames(table_val))
      for (k in (1:length(values_pred))){
            good_pred = table_val[values_pred[k],k]
       }
      
      accuracy_thresh_perturbed = good_pred/n
      
      robust_accuracy_p <- c(robust_accuracy_p, accuracy_thresh_perturbed )
  
}
write.csv(robust_accuracy_p, "robust_accuracy_p.csv")
write.csv(seq_pertubation, "seq_pertubation.csv")
```


### NON REGULARIZED LOGISTIC REGRESSION PERFORMANCE

```{r }
x.train = model.matrix(best_treatment ~., data=utilities_train)
x.test = model.matrix(best_treatment ~., data=utilities_test)
y.train = utilities_train$best_treatment
y.test = utilities_test$best_treatment
set.seed(1)
#glm_treatment.cv <- cv.glmnet(x.train, y.train, alpha=1, family="multinomial", intercept = F, nfolds = 5)
        
#glm_treatment.min <- glm_treatment.cv$lambda.min
#glm_treatment.1se <- glm_treatment.cv$lambda.1se
   
glm_treatment.min = 0.0
glm_treatment <- glmnet(x.train,y.train,alpha=1,family="multinomial", lambda = glm_treatment.min, intercept = F)
# Definition of threshold
pred_in <- predict(glm_treatment,newx=x.train,type = 'response')
pred_in.df <- data.frame(pred_in)
best_threshold <- multi_threshold(pred_in.df, y.train)
### OUT-SAMPLE
pred <- data.frame(predict(glm_treatment,newx=x.test,type = 'response'))
best_out_accuracy <- threshold_accuracy(pred, y.test, 0.5)
```
```{r}
multi_pred <- function(pred){
    prediction <- c()
    for (i in 1:nrow(pred)) {
      val <- c(pred[i,1], pred[i,2], pred[i,3])
      prediction <- c(prediction, which.max(val))
    }
    return(prediction)
}
```

```{r }
seq_pertubation = seq(from = 0, to = 3, by = 0.1)
m = length(colnames(utilities_test)) 
n = nrow(utilities_test) #Here it's 3000
robust_accuracy_p_nr <- c()
for (p in seq_pertubation){
      utilities_test_perturbed = data.frame(utilities_test$best_treatment)
      for (i in 1:(m-1)){
      perturbation = data.frame(utilities_test[,m-i] + (means_global[m-i]-rnorm(n,means_global[m-i], p*sds_global[m-i] )))
      utilities_test_perturbed = data.frame(perturbation,utilities_test_perturbed)
      
      }
    
      colnames(utilities_test_perturbed) = colnames(utilities_test)
      
      x.test.perturbed = model.matrix(best_treatment ~., data=utilities_test_perturbed)
      y.test.perturbed  = utilities_test_perturbed$best_treatment
     
      prediction_perturbed = data.frame(predict(glm_treatment,newx=x.test.perturbed,type = 'response'))
      
      prediction_val = multi_pred(prediction_perturbed)
     
      table_val = table(y.test.perturbed, prediction_val)
      values_pred = as.numeric(colnames(table_val))
      for (k in (1:length(values_pred))){
            good_pred = table_val[values_pred[k],k]
       }
      
      accuracy_thresh_perturbed = good_pred/n
      
      robust_accuracy_p_nr <- c(robust_accuracy_p_nr, accuracy_thresh_perturbed )
  
}
write.csv(robust_accuracy_p_nr, "robust_accuracy_p_nr.csv")
write.csv(seq_pertubation, "seq_pertubation_nr.csv")
```



